---
title: "Ms Draft: The biodiversity of plant-frugivore interactions: types, functions, and consequences"
author:
  name: Pedro Jordano
  affiliation: 
    name: Estación Biológica de Doñana, CSIC and Dept. Biol. Vegetal y Ecología, Universidad de Sevilla
date: 2025-01-21
toc: false
orcid: 0000-0003-2142-9116
email: jordano@ebd.csic.es
city: Sevilla
url: pjordanolab.ebd.csic.es
abstract: "Pairwise plant-frugivore mutualistic interactions build up into mega-diverse networks involving dozens of interacting species, being the most generalized among free-living species. These mutualisms consist of food provisioning by plants and, their counterpart, plant propagule (seeds) movement by the animals, being crucial for the natural vegetation regeneration in many ecosystems. Yet we are far from understanding which part of this enormous interaction biodiversity is needed for their maintenance.
I overview the diversity of interaction modes involved in these mutualisms, the main components of the seed dispersal services, and their functional diversity. I examine how interaction richness covaries with partner species richness at different scales, resulting in variable patterns of species complementarities in terms of seed dispersal effects. The functionality of most generalized plant-frugivore mutualisms relies on complementarity of effects across a high diversity of partners, yet frequently depends on just a distinct subset of them, resulting in high functional redundancy. Two distinct aspects are relevant: 1) variable quantitative effects among species; 2) variable parwise-interaction outcomes, between the extremes of antagonism and mutualism."
keywords:
        seed dispersal
        mutualism
        plant-animal interactions
        frugivory
license: "CC BY-NC" 
copyright: 
        holder: Pedro Jordano
year: 2008
citation: 
        container-title: Oikos
volume: 00
issue: 0
doi: 00.0000/00000000
output: html_document
format: 
   pdf:
      documentclass: article
      papersize: a4
      classoption: [11pt]
      fig-width: 8
      fig-height: 6
      geometry:
        - top=20mm
        - left=25mm
        - right=15mm
        - textwidth=130mm
filters:
  - multibib    # install from https://github.com/pandoc-ext/multibib
validate-yaml: false 
code-fold: TRUE
bibliography: 
          main: ms.bib
          software: grateful-refs.bib
citeproc: false
csl: oikos.csl
editor_options: 
  chunk_output_type: console
---

{{< pagebreak >}}

```{r setup, echo=F, warning=F, message=FALSE, include=FALSE}
library(knitr)
library(here)           
library(tidyverse)
library(dplyr)
library(lme4)
library(equatiomatic)
library(kableExtra)
library(easystats)
library(report)
library(ggcorrplot)
library(rstatix)
library(gridExtra)
library(FD)
library(latex2exp)
library(grateful)
#-----------------------------------------------------------------
### Chunk options ###
## Text results
opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, size = 'tiny')
## Code decoration
opts_chunk$set(tidy = FALSE, comment = NA, highlight = TRUE, prompt = FALSE, crop = TRUE)
# ## Cache
opts_chunk$set(cache = TRUE)
# ## Plots
# opts_chunk$set(fig.path = 'knitr_output/figures/')
opts_chunk$set(fig.align = 'center', out.width = '98%')
### Hooks ###
## Crop plot margins
knit_hooks$set(crop = hook_pdfcrop)
## Reduce font size
## use tinycode = TRUE as chunk option to reduce code font size
# see http://stackoverflow.com/a/39961605
# knit_hooks$set(tinycode = function(before, options, envir) {
#     if (before) return(paste0('\n \\', options$size, '\n\n'))
#     else return('\n\n \\normalsize \n')
#     })
# def.chunk.hook  <- knitr::knit_hooks$get("chunk")
# knitr::knit_hooks$set(chunk = function(x, options) {
#   x <- def.chunk.hook(x, options)
#   paste0("\n \\", "footnotesize","\n\n", x, "\n\n \\Huge")
# })

```

### Interaction richness and diversity

R code for summarizing relationships between species richness ($S= P + A$) and interaction
richness ($I$) in plant-frugivore assemblages, as well as other metrics for input
datasets. Data include $N=$ 165 assemblages, ranging from local to regional and
biome-scale.

```{r input}
# here()
mypath<- here(c("data/data.tsv"))
data1 <- read.csv(mypath, sep="\t", dec=",", header=T, 
				  comment.char = "#")
# data <- data %>% 
#	         arrange(sp_plant, desc(pct_mut))

```

```{r plots, ECHO=TRUE, warning=F, fig.width=12,fig.height=8}
# here()
# Scatter plot
theme_set(theme_bw(base_size = 18))
p1<- ggplot(data1, aes(x= S, y= I, color=biome, shape= type)) + 
	        geom_point(size= 4) +
			geom_point(aes(color= biome), size= 4.5, color= "black") +
#			geom_point(aes(color= biome), size= 5) +
			geom_point(aes(color= biome), size= 3) +
  	        scale_x_continuous(trans='log10') +
	        scale_y_continuous(trans='log10') +
	        scale_color_manual(values=c("#5681DC", "#DEA525")) +
		    ggplot2::labs(color = "Biome") +
            ggplot2::labs(x = TeX(r"(Number of species, \textit{S})"), 
  	            y = TeX(r"(Number of distinct, pairwise interactions, \textit{I})")) 
p1

```

#### Model fit, pooled data

`glm` model for the regression lines.

```{r regr, echo=TRUE}
m1 <- lm(log(I) ~ log(S), data = data1)
equatiomatic::extract_eq(m1)
equatiomatic::extract_eq(m1, use_coefs = TRUE)
summary(m1)
parameters::parameters(m1)


# Separate effects of Animal and Plant species richness on I.
# 
m2 <- lm(log(I) ~ log(P)+log(A), data = data1)
equatiomatic::extract_eq(m2)
equatiomatic::extract_eq(m2, use_coefs = TRUE)
summary(m2)
parameters::parameters(m2)

```

#### Summary stats, by biome

```{r summ_data_biome}
library(rstatix)

# Summary statistics for dependent variable yield 
ppp<- data1 %>% group_by(biome) %>% get_summary_stats(c(A,P,S,I,C), type="common")
ppp_srt<- ppp |>
            arrange(variable, biome)
kable(ppp_srt)


# Separate regressions for biomes
# 
# Tropical
ppp<- data1 %>% dplyr::filter(biome== "t")
m2<- lm(log(I) ~ log(S), data = ppp)
equatiomatic::extract_eq(m2)
equatiomatic::extract_eq(m2, use_coefs = TRUE)
summary(m2)
parameters::parameters(m2)

# Non-tropical
ppp<- data1 %>% dplyr::filter(biome== "nt")
m3 <- lm(log(I) ~ log(S), data = ppp)
equatiomatic::extract_eq(m3)
equatiomatic::extract_eq(m3, use_coefs = TRUE)
summary(m3)
parameters::parameters(m3)

```

#### ANCOVA test

```{r ancova_biome}
kable(anova_test(data = data1, formula = log(I) ~ log(S) + biome, type = 3, detailed = TRUE)) 
# Type 3 SS should be used in ANCOVA
kable(Anova(aov(log(I) ~ biome * log(S), data = data1), type = 3))

```

#### Summary stats, by type, sp-based vs. ind-based

```{r summ_data_type}
library(rstatix)
# summary statistics for dependent variable yield 
ppp<- data1 %>% group_by(type) %>% get_summary_stats(c(A,P,S,I,C), type="common")
ppp_srt<- ppp |>
            arrange(variable, type)
kable(ppp_srt)

# Separate regressions for sp-based and ind-based networks
# 
# Species-based
ppp<- data1 %>% dplyr::filter(type== "sp")
m3<- lm(log(I) ~ log(S), data = ppp)
equatiomatic::extract_eq(m3)
equatiomatic::extract_eq(m3, use_coefs = TRUE)
summary(m3)
parameters::parameters(m3)

# Individual-based
ppp<- data1 %>% dplyr::filter(type== "ind")
m4 <- lm(log(I) ~ log(S), data = ppp)
equatiomatic::extract_eq(m4)
equatiomatic::extract_eq(m4, use_coefs = TRUE)
summary(m4)
parameters::parameters(m4)

```

#### ANCOVA test

```{r ancova_type}
kable(anova_test(data = data1, formula = log(I) ~ log(S) + type + type * log(S), 
                 type = 3, detailed = TRUE)) 
# Type 3 SS should be used in ANCOVA
kable(Anova(aov(log(I) ~ type * log(S), data = data1), type = 3))

```

# Interaction richness and functional traits

Here I examine the functional characteristics of frugivore asemblages using two species,
*Prunus mahaleb* [@Jordano.Schupp:2000] and *Euterpe edulis* [@Galetti.etal:2013:S].
First, I examine how variation in functional traits of frugivore species and the resulting
interaction effectiveness generate gradients of interaction outcomes ranging from purely
mutualistic to purely antagonistic effects on fitness. Second, I show how the functional
diversity increases as the species richness of the frugivore assemblage increases.

Additional data for functional traits come from @Jordano.ea:2025:Ard,
@Bovo.Ferraz.ea:2018, and @Galetti.etal:2013:S.

### The distribution of functional interaction outcomes

Here I show the frequency distributions of mutualistic outcomes for the two species.
Individual frugivore species are ranked from those with 100% mutualistic interaction
outcomes (no fruits dropped or seeds damaged during foraging) to those with purely
antagonistic outcomes (100% of the feeding sequences ending in fruit dropping and/or seed
predation).

```{r input.gradient, ECHO=TRUE, warning=F, fig.width=12,fig.height=8}
# here()
mypath<- here(c("data/frug-mut_gradient.tsv"))
data2 <- read.csv(mypath, sep="\t", dec=",", header=T, 
				  comment.char = "#")

data2 <- data2 %>% 
	         arrange(sp_plant, desc(pct_mut))

theme_set(theme_bw(base_size = 18))
p <- ggplot(data2, aes(x = 1:nrow(data2), y = pct_mut,
					  color = sp_plant)) +
            	        geom_point(size= 4) +
			geom_point(aes(color= sp_plant), size= 4.5, color= "black") +
#			geom_point(aes(color= biome), size= 5) +
			geom_point(aes(color= sp_plant), size= 3) +
         #   geom_point(size=3.5) +
		    labs(color = "Plant species") +
	        scale_color_manual(values=c("#DEA525","#5681DC")) +
            labs(x = "Index")

p + geom_rug(sides = "rl", color = "black")

```

### Functional diversity as a function of assemblage species richness

For the two species, I include data on frugivore trait variation, local abundance,
visitation frequency to the trees, percent contribution to seed dispersal, measures of the
quantitative component of seed dipersal effectiveness `SDE` (effectiveness per visit,
visit frequency, and total effectiveness) and species-specific contribution to FD of the
assemblage.

```{r morpho}
# Input functional datasets.
# here()
#---------------------------------------------------------------------
## Euterpe edulis
mypath<- here(c("data/funct.csv"))
funct<- read.csv(mypath, sep=",", dec=".", header=T, 
				  comment.char = "#")
funct_euterpe<- funct %>% 
					dplyr::filter(plant == 'Euterpe_edulis')  %>%
                    dplyr::select(species,frug:gape,pct_mut:prop_disp_service)
#					dplyr::select(species,frug:prop_disp_service)

m_e<- as.matrix(funct_euterpe[,2:6]) 
sp.names<- funct_euterpe[,1]
rownames(m_e)<- sp.names

a_e<- funct %>%               # Visitation (abund.)
			dplyr::filter(plant == 'Euterpe_edulis')  %>%
			dplyr::select(species,birds.km)
a_e<- t(a_e[,2])
colnames(a_e)<- sp.names

# Observed FD indices.
FDcomp_e <- functcomp(m_e, a_e)
ex_e<-dbFD(m_e, a_e, w.abun=TRUE, calc.FRic=TRUE, calc.FDiv= TRUE,
           corr= "cailliez", messages= TRUE)

#---------------------------------------------------------------------
# Prunus mahaleb
mypath<- here(c("data/funct.csv"))
funct <- read.csv(mypath, sep=",", dec=".", header=T, 
				  comment.char = "#")
funct_prunus<- funct %>% 
					dplyr::filter(plant == 'Prunus_mahaleb')  %>%
                    dplyr::select(species,frug:gape,pct_mut:prop_disp_service)
#					dplyr::select(species,frug:prop_disp_service)
m_p<-as.matrix(funct_prunus[,2:6])
sp.names<- funct_prunus[,1]

rownames(m_p)<- sp.names

a_p<- funct %>%               # Visitation (abund.)
			dplyr::filter(plant == 'Prunus_mahaleb')  %>%
			dplyr::select(species,birds.km)
sp.names<- a_p[,1]
a_p<- t(a_p[,2])
colnames(a_p)<- sp.names

# Observed FD indices.
FDcomp_p <- functcomp(m_p, a_p)
ex_p<- dbFD(m_p, a_p, w.abun=TRUE, calc.FRic=TRUE, calc.FDiv= TRUE,
           corr= "cailliez", messages = TRUE)

```

Here I create simulated assemblages of increasing species richness, between 5 species and
the total species number in each assemblage. For each species richness value I get the
mean and 1se values for the `FD` indexes. Each assemblage of 5, 6, 7, ... $S$ species is
generated by bootstrapping (without replacement) the original trait-data matrix.

### Bootstrap `FD` indices-*Euterpe edulis*

```{r boot_euterpe, message=F, warning=F, class.message= F}
# Install and load the boot package
library(boot)

# Create datasets of increasing no. species.
# Create a list to hold the samples.
# This gets as many samples as species, in 1 sp steps. With
# replacement. Loop this for N= 1000.
#
# This filters the abundance dataset so that the species included 
# in the abund data are the same as those in the morpho-boot data.
# Filter rows in a_e where species matches any species name in the
# boot-sample.

ta_e<- as.data.frame(t(a_e)) # Transposed abundance data to get 
                           # the spp names.
colnames(ta_e)<- c("abund")

# Initialize an empty data frame
dfe <- data.frame(run= integer(), i= integer(), 
				  FRic = numeric(), FEve = numeric(), 
				  FDis = numeric(),
				  RaoQ = numeric(), FDiv = numeric())
for (run in 1:10) {
	# Loop to create assemblages along a sequence of increasing
	# species richness. From 3 spp to the actual species richness
	# in the assemblage.
	for (i in 5:dim(m_p)[1]) {
		boot_sample<- lapply(1:dim(m_e)[1], function(i) {
		m_e[sample(nrow(m_e), i, replace = FALSE), ] })
	}
	# For each richness value, estimate FD indices. 
	for (i in 5:dim(m_p)[1])   {
			thesample= boot_sample[[i]]
			thesample.srt <- thesample[order(rownames(thesample)), ]
			filtered_a_e <- ta_e %>%     # Filtered abundances
				dplyr::filter(row.names(ta_e) %in% 
							  	row.names(boot_sample[[i]]))
			filtered_a_e.srt<- 
				t(filtered_a_e[order(rownames(filtered_a_e)), ])
			colnames(filtered_a_e.srt)<- 
				row.names(thesample.srt)
			z<- dbFD(thesample.srt, filtered_a_e.srt, 
					 w.abun=TRUE, calc.FRic=TRUE, 
					 calc.FDiv= TRUE, corr= "cailliez", messages = FALSE)
	 # Append indeces values for i and runs.
			dfe <- rbind(dfe,c(run,i,z$FRic,z$FEve,z$FDis,z$RaoQ,z$FDiv))
	}
}
	colnames(dfe)<- c("run","i","FRic","FEve","FDis","RaoQ","FDiv")

#---------------------------------------------------------------------
# Calculate mean FD values scored by no. species, ignoring NA values
mean_by_no.sp_e <- dfe %>%
  dplyr::group_by(i) %>%
  dplyr::summarise(
  	m_FRic= mean(FRic, na.rm = TRUE),
  	se_FRic= sd(FRic, na.rm = TRUE) / sqrt(n()),
  	m_FEve= mean(FEve, na.rm = TRUE),
  	se_FEve= sd(FEve, na.rm = TRUE) / sqrt(n()),
    m_FDis= mean(FDis, na.rm = TRUE),
  	se_FDis= sd(FDis, na.rm = TRUE) / sqrt(n()),
    m_RaoQ= mean(RaoQ, na.rm = TRUE),
  	se_RaoQ= sd(RaoQ, na.rm = TRUE) / sqrt(n()),
    m_FDiv= mean(FDiv, na.rm = TRUE),
	se_FDiv= sd(FDiv, na.rm = TRUE) / sqrt(n())
  )
#-------------------------------------------------------------------
# FRic
theme_set(theme_bw(base_size = 14))
p1<- ggplot(mean_by_no.sp_e, aes(x = i, y = m_FRic)) +
	geom_smooth(method = "loess", se = TRUE, 
			alpha= 0.3, color= "steelblue", fill = "#757171") +
	geom_point(color = "black", fill = "#DEA525", size=3, shape = 21, stroke = 0.5) +
	labs(title = "Euterpe edulis FRic", 
		        x = "No. species", 
  	            y = "Functional richness (FRic)") 
# FDis
theme_set(theme_bw(base_size = 14))
p2<- ggplot(mean_by_no.sp_e, aes(x = i, y = m_FDis)) +
	geom_smooth(method = "loess", se = TRUE, 
			alpha= 0.3, color= "steelblue", fill = "#757171") +
	geom_point(color = "black", fill = "#DEA525", size=3, shape = 21, stroke = 0.5) +
	labs(title = "Euterpe edulis FDis", 
		        x = "No. species", 
  	            y = "Functional dispersion (FDis)") 

# grid.arrange(p1, p2, ncol= 2)

```

### Bootstrap `FD` indices-*Prunus mahaleb*

```{r boot_prunus, message=F, warning=F, class.message=F, comment=F}
# Install and load the boot package
library(boot)

# Create datasets of increasing no. species.
# Create a list to hold the samples.
# This gets as many samples as species, in 1 sp steps. With
# replacement. Loop this for N= 1000.
#
# This filters the abundance dataset so that the species included 
# in the abund data are the same as those in the morpho-boot data.
# Filter rows in a_e where species matches any species name in the
# boot-sample.

ta_p<- as.data.frame(t(a_p)) # Transposed abundance data to get 
                             # the spp names.
colnames(ta_p)<- c("abund")

# Initialize an empty data frame
dfp <- data.frame(run= integer(), i= integer(), 
				  FRic = numeric(), FEve = numeric(), 
				  FDis = numeric(),
				  RaoQ = numeric(), FDiv = numeric())
for (run in 1:10) {
	# Loop to create assemblages along a sequence of increasing
	# species richness. From 3 spp to the actual species richness
	# in the assemblage.
	for (i in 5:dim(m_p)[1]) {
		boot_sample<- lapply(1:dim(m_p)[1], function(i) {
		m_p[sample(nrow(m_p), i, replace = FALSE), ] })
	#}
	# For each richness value, estimate FD indices. 
	#	for (i in 3:dim(m_p)[1]   {
			thesample= boot_sample[[i]]
			thesample.srt <- thesample[order(rownames(thesample)), ]
			filtered_a_p <- ta_p %>%     # Filtered abundances
				dplyr::filter(row.names(ta_p) %in% 
							  	row.names(boot_sample[[i]]))
			filtered_a_p.srt<- 
				t(filtered_a_p[order(rownames(filtered_a_p)), ])
			colnames(filtered_a_p.srt)<- 
				row.names(thesample.srt)
			z<- dbFD(thesample.srt, filtered_a_p.srt, 
					 w.abun=TRUE, calc.FRic=TRUE, 
					 calc.FDiv= TRUE, corr= "cailliez", messages = FALSE)
	 # Append indeces values for i and runs.
			dfp <- rbind(dfp,c(run,i,z$FRic,z$FEve,z$FDis,z$RaoQ,z$FDiv))
		}
}
	colnames(dfp)<- c("run","i","FRic","FEve","FDis","RaoQ","FDiv")

#---------------------------------------------------------------------
# Calculate mean FD values scored by no. species, ignoring NA values
mean_by_no.sp_p <- dfp %>%
  dplyr::group_by(i) %>%
  dplyr::summarise(
  	m_FRic= mean(FRic, na.rm = TRUE),
  	se_FRic= sd(FRic, na.rm = TRUE) / sqrt(n()),
  	m_FEve= mean(FEve, na.rm = TRUE),
  	se_FEve= sd(FEve, na.rm = TRUE) / sqrt(n()),
    m_FDis= mean(FDis, na.rm = TRUE),
  	se_FDis= sd(FDis, na.rm = TRUE) / sqrt(n()),
    m_RaoQ= mean(RaoQ, na.rm = TRUE),
  	se_RaoQ= sd(RaoQ, na.rm = TRUE) / sqrt(n()),
    m_FDiv= mean(FDiv, na.rm = TRUE),
	se_FDiv= sd(FDiv, na.rm = TRUE) / sqrt(n())
  )
#---------------------------------------------------------------------
# FRic
theme_set(theme_bw(base_size = 14))
p3<- ggplot(mean_by_no.sp_p, aes(x = i, y = m_FRic)) +
	geom_smooth(method = "loess", se = TRUE, 
			alpha= 0.3, color= "steelblue", fill = "#757171") +
	geom_point(color = "black", fill = "#5681DC", size=3, shape = 21, stroke = 0.5) +
	labs(title = "Prunus mahaleb FRic", x = "No. species", 
  			 y = "Functional richness (FRic)") 
# FDis
theme_set(theme_bw(base_size = 14))
p4<- ggplot(mean_by_no.sp_p, aes(x = i, y = m_FDis)) +
	geom_smooth(method = "loess", se = TRUE, 
			alpha= 0.3, color= "steelblue", fill = "#757171") +
	geom_point(color = "black", fill = "#5681DC", size=3, shape = 21, stroke = 0.5) +
	labs(title = "Prunus mahaleb FDis", x = "No. species", 
  			 y = "Functional dispersion (FDis)") 
# grid.arrange(p3, p4, ncol= 2)
# 
# All plots of simulated assemblages. 
grid.arrange(p1, p2, p3, p4, nrow= 2, ncol= 2)

```

### Summary of `FD` indices, compared to simulated-assemblage values

```{r FD_summary}
# Table of FD results.
# Observed FD values.
pp<- as.data.frame(t(unlist(ex_e)))
obs_e<- pp %>% 
	dplyr::select(FRic,FEve,FDis,RaoQ,FDiv)
#---------------------------------------------------------------------
pp<- as.data.frame(t(unlist(ex_p)))
obs_p<- pp %>% 
	dplyr::select(FRic,FEve,FDis,RaoQ,FDiv)

obs_FD<- rbind(obs_e, obs_p)
obs_FD <- obs_FD %>%
  mutate(species = c("Euterpe edulis", "Prunus mahaleb")) %>%
  select(species, everything())

# Summary of simulated FD indices for the two species.
FD_by_spp<- rbind(mean_by_no.sp_e[dim(m_e)[1]-6,],
                  mean_by_no.sp_p[dim(m_p)[1]-6,])

FD_by_spp <- FD_by_spp %>%
  mutate(species = c("Euterpe edulis", "Prunus mahaleb")) %>%
  select(species, everything())

kable(FD_by_spp)

```

```{r MF1, echo=FALSE, include= FALSE, eval=FALSE}
# m_e<-funct_euterpe %>% 
# 					dplyr::filter(plant == 'Euterpe_edulis')  %>%
# 					dplyr::select(species,frug:pct_mut)
# funct_norm_e<- m_e %>%
# 	      mutate(plotID="EUTEDU")
# funct_norm_e<- function_normalization(data = m_e, fun_cols = 2:5, 
# 					   negative = NULL,
# 					   by_group = NULL)
# funct_norm_e<- funct_norm_e %>%
# 	      mutate(plotID=species)
# 
# a_e<- funct_euterpe %>%               # Visitation (abund.)
# 					dplyr::filter(plant == 'Euterpe_edulis')  %>%
# 					dplyr::select(species,vis.10h)
# colnames(a_e)<- c("species","abundance")
# a_e<- a_e %>%
# 	      mutate(plotID=species)
# 
# MF1_single(func_data = funct_norm_e[2:5], weight = 1,
# species_data = a_e)

```

### Correlation analysis for FD values

Here I examine the correlates of trait variables with species-specific contributions to
FD.

```{r corr_plots, eval= TRUE}
#---------------------------------------------------------------------
# Correlation plots.
 corr<- cor(log(funct[,c(4:13)]+1), use = "pairwise")
# pmat <- cor_pmat(corr)
 corr1 <- cor(log(funct_euterpe[,c(2:8)]+1))
 corr2 <- cor(log(funct_prunus[,c(2:8)]+1))
# pmat1<- cor_pmat(corr1)
# pmat2<- cor_pmat(corr2)


# Two species pooled.
kbl(corr) %>%
  kable_styling(bootstrap_options = "striped", 
                font_size = 6, full_width = T)

# Euterpe
kbl(corr1) %>%
  kable_styling(bootstrap_options = "striped", font_size = 10)

# Prunus
kbl(corr2) %>%
  kable_styling(bootstrap_options = "striped", font_size = 10)

# Two species pooled
 ggcorrplot(corr,
           hc.order = F,
   		  # p.mat = pmat,
           type = "lower",
   		   insig = "pch",
   		   digits= 3,
           lab = TRUE, lab_size= 3) + ggtitle("Two species")

#---------------------------------------------------------------------
# Add correlation coefficients
  theme_set(theme_bw(base_size = 12))
  p1<- ggcorrplot(corr1,
           hc.order = F,
  		  # p.mat = pmat1,
           type = "lower",
  		   insig = "pch",
  		   digits= 3,
           lab = TRUE, lab_size= 2) + ggtitle("Euterpe edulis")
  p2<- ggcorrplot(corr2,
           hc.order = F,
  		 #  p.mat = pmat2,
  		   insig = "pch",
           type = "lower",
           digits= 3,
           lab = TRUE, lab_size= 2) + ggtitle("Prunus mahaleb")
  grid.arrange(p1, p2, nrow = 2)

```

### FD and SDE

Here I examine the relationships between FD and seed dispersal effectiveness (SDE).

```{r SDE}
theme_set(theme_bw(base_size = 14))
p1<- ggplot(funct, aes(x= contrib_FD+1, y= eff_total+1, color=plant)) + 
	        geom_point(size= 4) +
			geom_point(aes(color= plant), size= 5, color= "black") +
#			geom_point(aes(color= plant), size= 5) +
			geom_point(aes(color= plant), size= 3) +
  	        scale_x_continuous(trans='log10') +
	        scale_y_continuous(trans='log10') +
	        scale_color_manual(values=c("#5681DC", "#DEA525")) +
		    ggplot2::labs(color = "Species") +
            ggplot2::labs(x = TeX(r"(Species-specific contribution to \textit{FD})"),
  	         y = TeX(r"(Seed dispersal effectivenness (quantitative), \textit{SDE_{Q}})")) 
p1

# Correlations for two species
cor.test(log(funct$contrib_FD+1),log(funct$eff_total+1))

# Euterpe edulis
pp<- funct %>%
    dplyr::filter(plant== "Euterpe_edulis")
    cor.test(log(pp$contrib_FD+1),log(pp$eff_total+1))


# Prunus mahaleb
pp<- funct %>%
    dplyr::filter(plant== "Prunus_mahaleb")
    cor.test(log(pp$contrib_FD+1),log(pp$eff_total+1))

```

------------------------------------------------------------------------------------------

# Multilayer analysis

|                                                                                          |
|:-----------------------------------------------------------------------------------------|
| \## NOTE:                                                                                |
| Code for multilayer analysis with the `muxViz` package is provided in a separate folder. |
| It requires specific installation of external binaries. I've run it on `R` version       |
| 4.0, since several required packages have not recent versions.                           |

{{< pagebreak >}}

------------------------------------------------------------------------------------------

# `R` packages used

```{r grateful}
#| echo: FALSE
#| message: FALSE
#| class.message: FALSE,
#| class.warning: FALSE,
#| warning: FALSE

grateful::cite_packages(pkgs = "Session", 
                        output = "paragraph", 
                        out.dir = ".", 
                        out.format= "pdf")

```

{{< pagebreak >}}

Session info

```{r session, warning=FALSE, error=FALSE}
sessionInfo()

```

{{< pagebreak >}}

# References

\normalsize

::: {#refs-main}
:::

# Software

\normalsize

::: {#refs-software}
:::
