---
title: "EMLN analysis"
author:
  name: Pedro Jordano
  affiliation: 
    name: Estación Biológica de Doñana, CSIC and Dept. Biol. Vegetal y Ecología, Universidad de Sevilla
toc: false
orcid: 0000-0003-2142-9116
email: jordano@ebd.csic.es
city: Sevilla
url: pjordanolab.ebd.csic.es
date: "2023-11-20"
output: pdf_document
format: 
   pdf:
      documentclass: article
      papersize: a4
      classoption: [11pt]
      fig-width: 8
      fig-height: 6
      geometry:
        - top=20mm
        - left=25mm
        - right=15mm
        - bottom=20mm
        - textwidth=130mm
code-fold: TRUE
bibliography: grateful-emln-refs.bib
editor_options: 
     chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
package.list=c("tidyverse", "magrittr","igraph","Matrix","DT","hablar","devtools")
loaded <-  package.list %in% .packages()
package.list <-  package.list[!loaded]
installed <-  package.list %in% .packages(TRUE)
if (!all(installed)) install.packages(package.list[!installed],
                                      repos="http://cran.rstudio.com/")
options(max.print = 1000000)
# devtools::install_github('Ecological-Complexity-Lab/emln', force=T)
library(here)
library(emln)
library(igraph)
library(bipartite)
library(magrittr)
library(ggplot2)
library(readr)
library(tibble)
library(dplyr)
library(readr)
library(stringr)
library(ggsci)
library(ggbreak)
# remotes::install_github("YuLab-SMU/ggbreak")
library(ggpubr)
library(ggbipart)
library(grateful)
library(ComplexHeatmap)

# Setup paths to external fanmod and infomap executables.
pathFanmod <- here::here("RCode/multiplex/src-exe/fanmod_macosx")
pathInfomap <- here::here("./RCode/multiplex/src-exe/Infomap")

```

## Data

Here I read the interaction data as data.frames imported from csv or tab-separated files.
Then I extract just the interaction matrices with the corresponding row names.

```{r input.prunus}
pm.disp<- read.table(here::here("data/raw/multiplex/pmah_disp.txt"), sep="\t",
                     dec=".", header= TRUE)
pm.poll<- read.table(here::here("data/raw/multiplex/pmah_poll.txt"), 
    na="NA", sep="\t", dec=".", header= TRUE)
pm.herb<- read.table(here::here("data/raw/multiplex/pmah_herb.txt"), 
     na="NA", sep="\t", dec=".", header= TRUE)
pm.attr<- read.table(here::here("data/raw/multiplex/pmah_attr.txt"), 
    na="NA", sep="\t", dec=".", header= TRUE)

# Interaction matrices extracted from the dataframes.
pm.herb.mat<- as.matrix(pm.herb[1:19,2:12], 
		ncol = n, dimnames = list(paste0("A", 1:12), paste0("P", 1:19)))
row.names(pm.herb.mat)<- pm.herb$X[1:19]

pm.poll.mat<- as.matrix(pm.poll[1:19,2:44], 
		dimnames = list(paste0("A", 1:44), paste0("P", 1:19)))
row.names(pm.poll.mat)<- pm.poll$X[1:19]

pm.disp.mat<- as.matrix(pm.disp[1:19,2:22], 
		dimnames = list(paste0("A", 1:22), paste0("P", 1:19)))
row.names(pm.disp.mat)<- pm.disp$X[1:19]

# Total number of distinct nodes (physical nodes). 
# Here the trees are counted just once.
dim(pm.herb.mat)[1]+dim(pm.herb.mat)[2]+dim(pm.poll.mat)[2]+dim(pm.disp.mat)[2]

# Total number of state nodes (trees). Here the trees are counted just once.
dim(pm.herb.mat)[1]

# Total number of nodes (physical and state). 
# Here the trees (state nodes) are counted three times, one state in each layer.
dim(pm.herb.mat)[1]+dim(pm.herb.mat)[2]+dim(pm.poll.mat)[1]+dim(pm.poll.mat)[2]+
    dim(pm.disp.mat)[1]+dim(pm.disp.mat)[2]

# Total number of interactions recorded
dim(pm.herb.mat); dim(pm.poll.mat); dim(pm.disp.mat)
sum(pm.herb.mat, pm.poll.mat, pm.disp.mat)
non_zero_count <- sum(pm.herb.mat != 0,   # Count non-zero elements. 
                                          # No. distinct interactions.
                      pm.poll.mat != 0, 
                      pm.disp.mat != 0) ; non_zero_count

# Convert a matrix to an edge list for bipartite network
pm.disp.bip<- matrix_to_list_bipartite(pm.disp.mat, 
                                       group_names = c('A_set', 
                                                       'P_set'))$edge_list

pm.poll.bip<- matrix_to_list_bipartite(pm.poll.mat, 
                                       group_names = c('A_set', 
                                                       'P_set'))$edge_list

pm.herb.bip<- matrix_to_list_bipartite(pm.herb.mat, 
                                       group_names = c('A_set', 
                                                       'P_set'))$edge_list

```

# Multilayer structure

This is code to create the multilayer structure.

```{r multilayer, echo= TRUE}
# Create the layers from the matrix. These are  the intra-layer interactions,
# based on the adjacency matrices.
herbivory_layer <- pm.herb.mat
pollination_layer <- pm.poll.mat
seed_dispersal_layer <- pm.disp.mat
	
layer_attrib <- tibble(layer_id=1:3,
                     layer_name=c('Herbivory','Pollination',
                     			  'Seed dispersal'),
                     Method=c('Observation','Collection','Observation'))

# Create the ELL tibble with interlayer links.
interlayer <- tibble(layer_from= c(rep('Herbivory',19),
								   rep('Pollination',19)),
                     node_from= c("pm1933","pm1931","pm1932","pm1934","pm1936",
                                  "pm1937","pm1938","pm1939","pm1940","pm1921",
                                  "pm1823","pm1824","pm1820","pm1825","pm1929",
                                  "pm8801","pm8808","pm8814","pm8865",
                                 "pm1933","pm1931","pm1932","pm1934","pm1936",
                                  "pm1937","pm1938","pm1939","pm1940","pm1921",
                                  "pm1823","pm1824","pm1820","pm1825","pm1929",
                                  "pm8801","pm8808","pm8814","pm8865"),
                     layer_to= c(rep('Pollination',19), 
							     rep('Seed dispersal',19)),
                     node_to= c("pm1933","pm1931","pm1932","pm1934","pm1936",
                                  "pm1937","pm1938","pm1939","pm1940","pm1921",
                                  "pm1823","pm1824","pm1820","pm1825","pm1929",
                                  "pm8801","pm8808","pm8814","pm8865",
                                 "pm1933","pm1931","pm1932","pm1934","pm1936",
                                  "pm1937","pm1938","pm1939","pm1940","pm1921",
                                  "pm1823","pm1824","pm1820","pm1825","pm1929",
                                  "pm8801","pm8808","pm8814","pm8865"),
					             weight= 1) # I'm assuming here 
                                            # interlayer links weights= 1.

# Create the multilayer. It has 132 nodes, counting the trees just as physical 
# nodes (only once).

multilayer_bip_pru <- create_multilayer_network(list_of_layers = 
					  list(herbivory_layer, pollination_layer, 
					       seed_dispersal_layer), 
					  bipartite = T, 
					  directed = F, 
					  interlayer_links = interlayer, 
					  layer_attributes = layer_attrib)

```

## emln Analysis. SAM matrix

Here I get the supra-adjacency matrix (SAM) and generate a the whole graph.

```{r emln, echo=TRUE, fig.height=12,fig.width=14}
library(emln)
library(tidyverse)
library(infomapecology)
library(magrittr)

# Get the SAM. Remove zero rows/cols and get a sparse matrix. This has 279 nodes, 
# including the trees counted three times and animals counted three times. The full
# list can found in multilayer_bip_pru$nodes and the complete list of nodes 
# (including the NAs of the large megamatrix, in: multilayer_bip_pru$state_nodes_map.
pru.sam_bipartite <- get_sam(multilayer = multilayer_bip_pru, bipartite = T,
                             directed = F, sparse = F, remove_zero_rows_cols = T)
dim(pru.sam_bipartite$M) # This is a 132x132 square supra-adjacency matrix.
pru.sam_bipartite$M

# Dimension of the supramatrix: 
# 
# Here I count all the trees three times and all the animals three times.
# The interactions between animals in layers where they are not present are 
# included in SAM as NAs.
SAM_dim<- (dim(pm.herb.mat)[1]*3)+ # Counts of trees
          (dim(pm.herb.mat)[2]*3)+
          (dim(pm.poll.mat)[2]*3)+
          (dim(pm.disp.mat)[2]*3)  ; SAM_dim

visweb(pru.sam_bipartite$M, type= "none",
       circles=TRUE, boxes=F, 
	   labsize=1, circle.max=1, circle.min=0.15,
       text="no", outerbox.border="black", circle.col="#5878A8", 
       box.col="lightgrey")
visweb(pru.sam_bipartite$M,
       circles=TRUE, boxes=F, 
	   labsize=1, circle.max=1.5, circle.min=0.25,
       text="no", outerbox.border="black", circle.col="#5878A8", 
       box.col="lightgrey")

# These are the unipartite graphs.
g_layers_bip <- get_igraph(multilayer = multilayer_bip_pru, bipartite = T, 
                           directed = F)
l1 <- g_layers_bip$layers_igraph[[1]]
l2 <- g_layers_bip$layers_igraph[[2]]
l3 <- g_layers_bip$layers_igraph[[3]]
l1; l2; l3

```

These are 3D heatmap plots of the supra-adjacency matrix.

```{r 3D, echo=TRUE, fig.height=14, fig.width=14}
# 3d heatmap
# 
mat<- pru.sam_bipartite$M
rownames(mat)<- c("pm1933","pm1931","pm1932","pm1934","pm1936","pm1937",
                  "pm1938","pm1939","pm1940","pm1921","pm1823","pm1824",
                  "pm1820","pm1825","pm1929","pm8801","pm8808","pm8814",
                  "pm8865","Yponomeuta.mahalebella","Hemaris.fuciformis",
                  "Iphiclides.podalirius","Hedya.pruniana","Orthoptera.NI",
                  "Myzus.cerasi","Aglaope.infausta","Fungus.NI",
                  "Taphrina.deformans","Ungulates","NI","pm1933","pm1931",
                  "pm1932","pm1934","pm1936","pm1937","pm1938","pm1939",
                  "pm1940","pm1921","pm1823","pm1824","pm1820","pm1825",
                  "pm1929","pm8801","pm8808","pm8814","pm8865",
                  "Hemaris.tityus","Iphiclides.podalirius","Vanessa.cardui",
                  "Psithyrus.vestalis.obenbergeri","Bombus.pratorum.m.",
                  "Bombus.pratorum.wk.","Bombus.pascuorum.wk.",
                  "Bombus.pascuorum.q.","Bombus.terrestris.wk.",
                  "Bombus.terrestris.q.","Xylocopa.violacea","Apis.mellifera",
                  "Osmia.rufa","Andrena.fulva","Andrena.synadelpha.nigroaenea",
                  "Andrena.trimmerana","Andrena.congruens",
                  "Andrena.tibialis.corvina","Andrena.albopunctata.morio",
                  "Andrena.assimilis","Halictus.quadricinctus",
                  "Halictus.tridivisus","Halictus.scabiosae",
                  "Lasioglossum.xanthopum","Sphecodes.gibbus",
                  "Megachile.centuncularis","Ancistrocerus.nigricornis",
                  "Eristalis.tenax","Eristalis.pratorum","Eristalis.arbustorum",
                  "Cheilosia.glossa","Mallota.fuciformis",
                  "Dasysyrphus.albostriatus","Syrphus.vitripennis",
                  "Syrphus.ribessi","Criorhina.berberina","Calliphora.vomitoria",
                  "Gonia.ornata","Pollenia.rudis","Tachina.corsicana",
                  "Asilidae.n.i.","Empididae.n.i.","Diptera.n.i.","pm1933",
                  "pm1931","pm1932","pm1934","pm1936","pm1937","pm1938",
                  "pm1939","pm1940","pm1921","pm1823","pm1824","pm1820",
                  "pm1825","pm1929","pm8801","pm8808","pm8814","pm8865",
                  "Columba.palumbus","Garrulus.glandarius","Turdus.merula",
                  "Phoenicurus.ochruros","Erithacus.rubecula","Parus.ater",
                  "Fringilla.coelebs","Sylvia.conspicillata",
                  "Sylvia.atricapilla","Turdus.viscivorus","Sylvia.communis",
                  "Sylvia.melanocephala","Sylvia.borin","Parus.caeruleus",
                  "Phoenicurus.phoenicurus","Parus.cristatus","Parus.major",
                  "Sylvia.cantillans","Sitta.europaea","Dendrocopos.major",
                  "Unidentified")

# Plot
col_fun = circlize::colorRamp2(c(0, 1, 2, 4, 6, 8), 
                               c("#FFFFFF", "#B3C0F5", "#7A93F5", 
                                 "#1E36EB", "#070F85","#082173"))
ht_opt$TITLE_PADDING = unit(c(10, 2), "mm")

# This takes time...
Heatmap3D(log(mat+1), name = c("Interaction frequency"), col = col_fun,
          cluster_columns = FALSE, show_row_dend = FALSE, 
          cluster_rows = FALSE,
          show_column_names = TRUE,
          heatmap_legend_param = list(at = c(0, 1, 2, 4, 6, 8), 
                                      labels = c("0", "30", "60", 
                                                 "90", "120",">150")),
          column_title = '      ',
          row_names_side = "left", 
          column_names_gp = gpar(fontsize = 9),
          border = TRUE,
          border_gp = gpar(col = "lightgrey"),
          row_names_gp = gpar(fontsize = 7),
          # new arguments for Heatmap3D()
          bar_rel_width = 1, bar_rel_height = 1, 
          bar_max_length = unit(0.7, "cm")
          )

```

## Comparing EC scores in monolayer and multilayer networks

Calculating the Eigenvector centrality score of each state node on a per-layer basis. Then
using a stack bar plot to include also the multilayer eigen-centralities.

```{r eigenv_centr_monolayer, echo= TRUE, fig.height=9, fig.width=12}
# Get a list of igraph objects as layers igraph 
g_layers_bip <- get_igraph(multilayer = multilayer_bip_pru, 
                           bipartite = T, directed = F)

# get Eigenvector scores of igraph layers
eigen_igraph_herb<- 
    igraph::eigen_centrality(g_layers_bip$layers_igraph$'Herbivory')$vector
eigen_igraph_poll<- 
    igraph::eigen_centrality(g_layers_bip$layers_igraph$'Pollination')$vector
eigen_igraph_disp<- 
    igraph::eigen_centrality(g_layers_bip$layers_igraph$'Seed dispersal')$vector

# Save the mono-layer eigenvector centralities
eigen_igraph_mono<- list(eigen_igraph_herb,eigen_igraph_poll,
                            eigen_igraph_disp)

eigenc_mono<- read.table(here::here("data/raw/multiplex/pm_eigen_centrality_mono.tsv"), 
                         sep="\t", dec=".", header= TRUE)

# Stackbar plots for monolayer centralities of the trees.
# TODO 
# Extract the trees
eigenc_mono_trees<- read.table(here::here(
    "data/raw/multiplex/pm_eigen_centrality_mono_trees.tsv"), 
    sep="\t", dec=".", header= TRUE)

#------------------------------------------------------------------
# Only trees eigenvector centrality.
eigenc_bar<- eigenc_mono_trees
colnames(eigenc_bar)<- c("layer","node","eigen.centrality")

# Plotting just the monolayer centralities, stacked.
ggplot(eigenc_bar, aes(x= reorder(node, -eigen.centrality), 
                       y=eigen.centrality, fill=layer))+
  geom_bar(stat="identity", width=1, col="white")+
  theme_bw()+
  scale_x_discrete(name="")+
  ggtitle("Trees eigenvector centrality") +
  theme(plot.title = element_text(face = "bold", size = 16, colour = "black", 
                                  hjust = 0.5, vjust = 1)) +
  scale_fill_manual(values=c("#5878A8", "#8EACDF", "#C6E4FF")) +
  coord_flip()

#-----------------------------------------------------------------
# The multilayer
#-----------------------------------------------------------------
# My function for bipartite graph.
bip_init_igraph <- function (mat) {
                require(igraph)
                igraph::graph_from_incidence_matrix(mat,
                        weighted= T, add.names= T)
}
#-----------------------------------------------------------------
# get the SAM
pru.sam_bipartite <- get_sam(multilayer = multilayer_bip_pru, bipartite = T, 
							 directed = F, sparse = F, remove_zero_rows_cols = T)

# converting SAM to igraph object
graph_sam.g <- bip_init_igraph(pru.sam_bipartite$M)
graph_sam.g 

#-----------------------------------------------------------------
# Tree multi-layer eigenvector centrality
# eigenc_bar2<-as.data.frame(eigenc_bar2)

# Get Eigenvector scores
eigen_sam.g <- igraph::eigen_centrality(graph_sam.g, directed = F, scale = T)$vector
# Extract the trees
cond<- c(1:19,94:112,187:205) 
eigen_SAM<- as.numeric(eigen_sam.g[cond])

# Merge to data frame eigenvector comparison
ec_comparison <- data.frame(eigen_SAM, eigenc_bar$eigen.centrality) ## CHECK!!!
colnames(ec_comparison) <- c("multilayer","monolayer")
ec_comparison$monolayer[4]  <- 0.8567376385295642 # Correct typo 
                                                  # in tree pm1934.
                                                  # in tree pm1934.
eigen_igraph<- ec_comparison[,2]
eigen_multi_trees<- eigen_igraph[1:19]


eigen_multi_trees<- as.data.frame(eigen_multi_trees)
colnames(eigen_multi_trees)<- c("Multilayer")
eigen_multi_trees[4,]<- 0.8567376385295642   # Correct typo 
                                             # in tree pm1934.

xx<- data.frame(cbind(rep("Multilayer",19),
                      eigenc_bar$node[1:19],
                      eigen_multi_trees$Multilayer))
colnames(xx)<- c("layer","node","eigen.centrality")

# Alter column formats
xx <- xx %>%
  mutate(
    layer = as.character(layer),
    node = as.character(node),
    eigen.centrality= as.numeric(eigen.centrality)
  )

eigen_centr <- xx %>%
bind_rows(eigenc_bar)
levels(as.factor(eigen_centr$layer))
eigen_centr$layer<- factor(eigen_centr$layer, levels=c('Multilayer', 
                                                       'Herbivory',
                                                       'Pollination', 
                                                       'Seed dispersal'))

ggplot(eigen_centr, aes(x= reorder(node, -eigen.centrality), 
                        y= eigen.centrality, fill=layer))+
  geom_bar(stat="identity", width=1, col="white")+
  scale_fill_manual(values=c("#00325B", "#5878A8", "#8EACDF", "#C6E4FF")) +
  theme_bw()+
  scale_x_discrete(name="")+
  ggtitle("Trees multilayer eigenvector centrality") +
  theme(plot.title = element_text(face = "bold", size = 16, colour = "black", 
                                  hjust = 0.5, vjust = 1)) +
  coord_flip()

####################

```

Now calculating the eigenvector centrality score of each state node (the trees) using a
SAM of the multilayer network. Then I compare the multilayer eigenv-centrality with the
monolayer centralities.

```{r eigenv_centr_comparison, echo= TRUE, fig.height=12,fig.width=14}
# Scatter plot for eigenvector centralities comparison
ggplot(data = ec_comparison, aes(monolayer, multilayer)) + 
           	geom_point(aes(color= "#00325B"), size= 5, color= "black") +
            geom_point(color = "#859BF2", size = 3) + 
           labs(title = "Multilayer Eigenvector Centrality (EC) comparison", 
                x = "EC (monolayer)", y = "EC (multilayer)")+
  geom_abline()+
  scale_x_continuous(limits = c(0,1))+
  scale_y_continuous(limits = c(0,1))+
  coord_fixed() +
  theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.title = element_text(size=15),
        axis.text = element_text(color='black',size = 10),
        legend.text =  element_text(size=15),
        legend.title = element_text(size=20))

```

The deviation of the points from the reference line indicates a lack of correlation
between the two centrality scores. We see that the majority of the nodes that are
important in a monolayer, lose this importance in the multilayer network. There is also a
group of species that are important in both network types (upper right corner). This
highlights the value of considering the unique ecological processes and interactions
represented by different layers when analyzing multilayer networks and interpreting node
importance.

### Strength comparison

```{r}
#|> echo= TRUE
#|> fig.height= 9
#|> fig.width= 12

# Data 
strength<- read.table(here::here("RCode/multiplex/emln_input/strength.csv"), 
                         sep=",", dec=".", header= TRUE)

# Stack the outcome columns
strength_df1 <- strength %>%
  dplyr::filter(node==c(1:19)) %>% 
  pivot_longer(
    cols = c(layer1, layer2, layer3),
    names_to = "layer",
    values_to = "strength")

# Scatter plot for eigenvector centralities comparison
ggplot(data = strength_df1, aes(agg, strength)) + 
			geom_point(aes(color= "#00325B"), size= 5, color= "black") +
            geom_point(color = "#859BF2", size = 3) + 
              labs(title = "Multilayer strength comparison", 
                x = "Strength (multilayer)", y = "Strength (monolayer)")+
  geom_abline()+
  coord_fixed() +
  theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.title = element_text(size=15),
        axis.text = element_text(color='black',size = 10),
        legend.text =  element_text(size=15),
        legend.title = element_text(size=20))

# Stack the outcome columns adding the data for multilayer strength.
strength_df2 <- strength %>%
  dplyr::filter(node==c(1:19)) %>% 
  pivot_longer(
    cols = c(agg, layer1, layer2, layer3),
    names_to = "layer",
    values_to = "strength")

strength_df <- strength_df2 %>%
mutate(layer = recode(layer, 'agg'= 'Multilayer', 'layer1' = 'Herbivory', 
                         'layer2' = 'Pollination', 
                         'layer3' = 'Seed dispersal'))

strength_df$layer<- as.factor(strength_df$layer)
strength_df$layer<- factor(strength_df$layer, levels=c('Multilayer', 
                                                       'Herbivory',
                                                       'Pollination', 
                                                       'Seed dispersal'))

strength_df$tree<- rep(c("pm1933","pm1931","pm1932","pm1934","pm1936",
                     			  "pm1937","pm1938","pm939","pm1940","pm1921",
                     			  "pm1823","pm1824","pm1820","pm1825","pm1929",
                     			  "pm8801","pm8808","pm8814","pm8865"), each = 4  )
ggplot(strength_df, aes(x= reorder(tree, -strength), 
                        y= strength, fill=layer))+
  geom_bar(stat="identity", width=1, col="white")+
  scale_fill_manual(values=c("#00325B", "#5878A8", "#8EACDF", "#C6E4FF")) +
  theme_bw()+
  scale_x_discrete(name="")+
  ggtitle("Trees multilayer strength") +
  theme(plot.title = element_text(face = "bold", size = 16, colour = "black", 
                                  hjust = 0.5, vjust = 1)) +
  coord_flip()

```

### Modularity SAM with bipartite

Modularity with bipartite SAM network and with infomap.

```{r multilayer_modularity, echo= TRUE, fig.height=12,fig.width=14}
# NOT RUN ###################################################################
#library(emln)
#install_infomap()
source(here::here("RCode/functions/my_run_infomap_multilayer.R"))
result <- my_run_infomap_multilayer(
    M = multilayer_bip_pru,
    infomap_executable = "Infomap", # pathto Infomap
    flow_model = "undirected", # Specify flow model explicitly
    silent = FALSE, # Enable verbose output for debugging
    trials = 100,
    relax = TRUE, # Disable relaxation if input format is extended
    run_standalone=T) # Run standalone execution
# NOT RUN ###################################################################
# 

# Testing modularity significance (@30 min for 100 null replicates)
require(bipartite)
TIME <- Sys.time()
mat <- pru.sam_bipartite$M     # Assign the observed matrix
node_names_supramux_132<- 
    read.table(here::here("./data/raw/prunus_data/node_names_supramux_132.txt"))
rownames(mat)<- node_names_supramux_132[,1]

res <- computeModules(mat) # Modularity for observed matrix
nulls <- nullmodel(mat, N=5, method=3)
modules.nulls <- sapply(nulls, computeModules)
like.nulls <- sapply(modules.nulls, function(x) x@likelihood)
z <- (res@likelihood - mean(like.nulls))/sd(like.nulls)
p <- 2*pnorm(-abs(z))
cat("M= ", res@likelihood)
cat("P= ",sprintf("%E", p))
Sys.time() - TIME 

printoutModuleInformation(res)

plotModuleWeb(res, plotModules = TRUE, 
rank = FALSE, weighted = TRUE, displayAlabels = TRUE, 
displayBlabels = TRUE, labsize = 0.5, xlabel = "", ylabel = "", 
square.border = "white", fromDepth = 0, upToDepth = -1)

# Print the whole network to assess node names
pru.sam_bipartite %>% print(n=Inf, na.print = "<NA>")

```

------------------------------------------------------------------------------------------

{{< pagebreak >}}

### Software used

```{r echo=FALSE}
pkgs <- grateful::cite_packages(output = "table", pkgs = "Session", out.dir = ".")
knitr::kable(pkgs)

```

{{< pagebreak >}}

### Session info

```{r session, echo= FALSE, warning=FALSE, error=FALSE}
sessionInfo()

```

## References
