---
title: "Multiplex analysis-Prunus mahaleb- with Infomap"
author:
  name: Pedro Jordano
  affiliation: 
    name: Estación Biológica de Doñana, CSIC and Dept. Biol. Vegetal y Ecología, Universidad de Sevilla
toc: false
orcid: 0000-0003-2142-9116
email: jordano@ebd.csic.es
city: Sevilla
url: pjordanolab.ebd.csic.es
date: "2023-11-23"
output: pdf_document
format: 
   pdf:
      documentclass: article
      papersize: a4
      classoption: [11pt]
      fig-width: 8
      fig-height: 6
      geometry:
        - top=20mm
        - left=25mm
        - right=15mm
        - bottom=20mm
        - textwidth=130mm
code-fold: TRUE
bibliography: grateful-infomap-refs.bib
editor_options: 
     chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#----------------------------------------------------------------------------------------------
library(here)
library(dplyr)
library(bipartite)
library(multinet)
library(igraph)
library(MuMIn)
library(mgcv)
library(performance)
library(muxViz)
library(rsq)
library(rgl)
library(viridis)
library(lme4)
library(GGally)
library(intergraph)
library(RColorBrewer)
library(ggraph)
library(ggbipart)
library(ggcorrplot)
library(infomapecology)
library(emln)
library(ComplexHeatmap)
#----------------------------------------------------------------------------------------------
# Setup paths to external fanmod and infomap executables.
pathFanmod <- here::here("RCode/multiplex/src-exe/fanmod_macosx")
pathInfomap <- here::here("RCode/multiplex/src-exe/Infomap")

```

## Data

Reading the multilayer network (dataframe) with three separate files, one for each type of
interaction. The data are read as square, weighted adjacency matrices to avoid problems
and limitations in infomap. I'm using the `emln` setup to get a multiplex arrangement to
be analizwd for multilayer modularity with `infomap` (shell binary executable).

```{r data, echo=TRUE}
# Data from raw interaction matrices. 
pm.herb<- read.table(here::here("data/raw/multiplex/pmah_herb.txt"), 
     na="NA", sep="\t", dec=".", header= TRUE)
pm.poll<- read.table(here::here("data/raw/multiplex/pmah_poll.txt"), 
    na="NA", sep="\t", dec=".", header= TRUE)
pm.disp<- read.table(here::here("data/raw/multiplex/pmah_disp.txt"), sep="\t",
                     dec=".", header= TRUE)
pm.attr<- read.table(here::here("data/raw/multiplex/pmah_attr.txt"), 
    na="NA", sep="\t", dec=".", header= TRUE)

# Interaction matrices extracted from the dataframes.
pm.herb.mat<- as.matrix(pm.herb[1:19,2:12], 
        ncol = n, dimnames = list(paste0("A", 1:12), paste0("P", 1:19)))
row.names(pm.herb.mat)<- pm.herb$X[1:19]

pm.poll.mat<- as.matrix(pm.poll[1:19,2:44], 
        dimnames = list(paste0("A", 1:44), paste0("P", 1:19)))
row.names(pm.poll.mat)<- pm.poll$X[1:19]

pm.disp.mat<- as.matrix(pm.disp[1:19,2:22], 
        dimnames = list(paste0("A", 1:22), paste0("P", 1:19)))
row.names(pm.disp.mat)<- pm.disp$X[1:19]

# Create the layers from the matrix. These are  the intra-layer interactions,
# based on the adjacency matrices.
herbivory_layer <- pm.herb.mat
pollination_layer <- pm.poll.mat
seed_dispersal_layer <- pm.disp.mat
    
layer_attrib <- tibble(layer_id=1:3,
                     layer_name=c('Herbivory','Pollination',
                                  'Seed dispersal'),
                     Method=c('Observation','Collection','Observation'))

# Create the ELL tibble with interlayer links.
interlayer <- tibble(layer_from= c(rep('Herbivory',19),
                                   rep('Pollination',19)),
                     node_from= c("pm1933","pm1931","pm1932","pm1934","pm1936",
                                  "pm1937","pm1938","pm1939","pm1940","pm1921",
                                  "pm1823","pm1824","pm1820","pm1825","pm1929",
                                  "pm8801","pm8808","pm8814","pm8865",
                                 "pm1933","pm1931","pm1932","pm1934","pm1936",
                                  "pm1937","pm1938","pm1939","pm1940","pm1921",
                                  "pm1823","pm1824","pm1820","pm1825","pm1929",
                                  "pm8801","pm8808","pm8814","pm8865"),
                     layer_to= c(rep('Pollination',19), 
                                 rep('Seed dispersal',19)),
                     node_to= c("pm1933","pm1931","pm1932","pm1934","pm1936",
                                  "pm1937","pm1938","pm1939","pm1940","pm1921",
                                  "pm1823","pm1824","pm1820","pm1825","pm1929",
                                  "pm8801","pm8808","pm8814","pm8865",
                                 "pm1933","pm1931","pm1932","pm1934","pm1936",
                                  "pm1937","pm1938","pm1939","pm1940","pm1921",
                                  "pm1823","pm1824","pm1820","pm1825","pm1929",
                                  "pm8801","pm8808","pm8814","pm8865"),
                                 weight= 1) # I'm assuming here 
                                            # interlayer links weights= 1.

# Create the multilayer. It has 132 nodes, counting the trees just as physical 
# nodes (only once).

multilayer_bip_pru <- create_multilayer_network(list_of_layers = 
                      list(herbivory_layer, pollination_layer, 
                           seed_dispersal_layer), 
                      bipartite = T, 
                      directed = F, 
                      interlayer_links = interlayer, 
                      layer_attributes = layer_attrib)
```

------------------------------------------------------------------------------------------

# Infomap

## Exploring modules on the three monolayer networks.

These are just the original, non-square matrices for each type of interaction. I'm using
this just to see the modular structure of each type of interaction analyzed with Infomap.

```{r monolayer_modul, echo=TRUE, fig.height= 10, fig.width= 12}
#----------------------------------------------------------------------------------------------
# Layer 1 - Herbivory interactions
pm.herb <- create_monolayer_network(pm.herb.mat, 
                                    bipartite = T, 
                                    directed = F, 
                                    group_names = c('A','P'))

pm.herb_object <- run_infomap_monolayer(pm.herb, 
                                        infomap_executable= "Infomap",
                                        flow_model = 'undirected',
                                        silent=T, trials=20, 
                                        two_level=T, seed=123)
colnames(pm.herb_object$edge_list)<- c("from","to","w")
# my_plot_modular_matrix(pm.herb_object)

#----------------------------------------------------------------------------------------------
# Layer 2 - Pollination interactions
pm.poll <- create_monolayer_network(pm.poll.mat, 
                                    bipartite = T, 
                                    directed = F, 
                                    group_names = c('A','P'))

pm.poll_object <- run_infomap_monolayer(pm.poll, 
                                        infomap_executable= "Infomap",
                                        flow_model = 'undirected',
                                        silent=T, trials=20, 
                                        two_level=T, seed=123)
#colnames(pm.poll_object$edge_list)<- c("from","to","w")
# my_plot_modular_matrix(pm.poll_object)
#----------------------------------------------------------------------------------------------
# Layer 3 - Seed dispersal interactions
pm.disp <- create_monolayer_network(pm.disp.mat, 
                                    bipartite = T, 
                                    directed = F, 
                                    group_names = c('A','P'))

pm.disp_object <- run_infomap_monolayer(pm.disp, 
                                        infomap_executable= "Infomap",
                                        flow_model = 'undirected',
                                        silent=T, trials=20, 
                                        two_level=T, seed=123)
# my_plot_modular_matrix(pm.disp_object)

```

## Multilayer network

Now, we will create the multilayer network. Although effectively it is a bipartite
network, we will treat it as an unipartite network to be able to account for link
directions. The description of function `create_multilayer_network` is in the package
emln. Plotting is done using two dedicated functions in infomapecology:
`plot_multilayer_modules` and `plot_multilayer_alluvial`.

```{r infomap2, echo=TRUE}
# Tree atributes dataset.
# Attributes file.
pm.attr<- read.table(here("./data/raw/prunus_data/pmah_attr.txt"), 
                     sep="\t", dec=".", header= TRUE)

require(forcats)
#pm.attr$pollen <- as.numeric(fct_relevel(data$ISLAND, "GC","TF","Go"))
pm.attr$pollen <- as.factor(fct_relevel(pm.attr$pollen, "n","+","++"))

#
# Create a multilayer object
#
layer_attrib <- tibble(layer_id=1:3, layer_name=c('Herbivory','Pollination','Dispersal'))                                     
pmah_interlayer <- read.table(here("./data/raw/multiplex/pmah_interlayer.csv"), 
                  header=TRUE, sep=",", dec = ".", quote = "", comment.char = "#")
pmah_layer_attr<- layer_attrib

multilayer_prunus <- create_multilayer_network(list_of_layers = list(pm.herb.mat,
                                                                      pm.poll.mat,
                                                                      pm.disp.mat),
                                              layer_attributes = pmah_layer_attr,
                                              interlayer_links = pmah_interlayer,       
                                              bipartite = T,
                                              directed = F, 
                                              physical_node_attributes = pm.attr)

```

# Multilayer community detection

```{r infomap_mod, echo=TRUE, fig.height= 9, fig.width= 12}
source(here::here("RCode/functions/my_run_infomap_multilayer.R"))
system("./Infomap ./out/multimap_prunus_infomap.edges ./out/ --clu --seed 12345 --num-trials 50 -v --multilayer-relax-rate 0.01, multilayerJSRelaxRate=NA, --two-level outputPrefix= multimap_prunus")

multilayer_bip_pru_modularity <- my_run_infomap_multilayer(M = multilayer_bip_pru,
						   relax = TRUE, silent = FALSE,
						   flow_model = "undirected",
						   trials = 50, seed = 497294,
						   twoLevel=T,
                           preclusterMultiplex=F,
                           addMissingPhysicalNodes=F,
						   multilayer_relax_rate = 0.01,
						   multilayer_relax_limit_up = 0.5,
						   multilayer_relax_limit_down = 0,
						   multilayerJSRelaxRate=NA,
						   temporal_network = FALSE)

# List of module composition
multilayer_bip_pru_modularity$m
module.comp<- print(multilayer_bip_pru_modularity$modules %>% 
	dplyr::select(node_id, layer_id, node_name, module), n=1000)
module.comp<- as.data.frame(module.comp)
#--------------------------------------------------------------------------
ggplot(multilayer_bip_pru_modularity$modules, aes(x= as.factor(module), 
												  y= node_name))+ 
	                                              geom_tile(aes(fill = flow),
                                colour = "white") + 
	                            scale_fill_gradient(low = "#75C4F5",
                                high = "#14374B") 

```

# Module assignement 3D plot

```{r 3D, echo=TRUE, fig.height=14, fig.width=5}
# 3d heatmap
# 
data<- multilayer_bip_pru_modularity$modules
str(data)

# Unstacking using pivot_wider()
df_wide <- pivot_wider(data, id_cols = node_name, names_from = module, values_from = flow)
str(df_wide)
head(df_wide)

df_wide.mat<- df_wide %>% select(3,4,5,2,8,6,7)
df_wide.mat<- as.data.frame(df_wide.mat)
df_wide.mat<- as.matrix(df_wide.mat)
rownames(df_wide.mat)<- df_wide$node_name
# Replace NA values with 0
df_wide.mat[is.na(df_wide.mat)] <- 0

# Plot
col_fun = circlize::colorRamp2(c(0, 0.005, 0.025, 0.05, 0.075, 0.1), 
                               c("#FFFFFF", "#B3C0F5", "#7A93F5", 
                                 "#1E36EB", "#070F85","#082173"))
ht_opt$TITLE_PADDING = unit(c(10, 2), "mm")
Heatmap3D(log(df_wide.mat+1), name = "strength", col = col_fun,
          cluster_columns = FALSE, show_row_dend = FALSE, 
          show_column_names = TRUE,
          heatmap_legend_param = list(at = c(0, 0.025, 0.05, 0.075, 0.1), 
                                      labels = c("0", "0.025", "0.05", " 0.075", "0.1")),
          column_title = '      ',
          row_names_side = "left", 
          row_names_gp = gpar(fontsize = 8),
          # new arguments for Heatmap3D()
          bar_rel_width = 1, bar_rel_height = 1, bar_max_length = unit(1.5, "cm")
          )

```

Thus modular arrangement can be compared with the one obtained with `bipartite` on the
flattened multilayer (in `emln` analysis).

------------------------------------------------------------------------------------------

{{< pagebreak >}}

# `R` packages used

```{r grateful}
#| echo: FALSE
#| message: FALSE
#| class.message: FALSE,
#| class.warning: FALSE,
#| warning: FALSE

pkgs <- grateful::cite_packages(output = "table", pkgs = "Session", out.dir = ".")
knitr::kable(pkgs)

```

{{< pagebreak >}}

# Session info

```{r session, warning=FALSE, error=FALSE}
sessionInfo()

```

{{< pagebreak >}}

# References

------------------------------------------------------------------------------------------
