---
title: "Multiplex_muxViz analysis-Prunus mahaleb"
author:
  name: Pedro Jordano
  affiliation: 
    name: Estación Biológica de Doñana, CSIC and Dept. Biol. Vegetal y Ecología, Universidad de Sevilla
toc: false
orcid: 0000-0003-2142-9116
email: jordano@ebd.csic.es
city: Sevilla
url: pjordanolab.ebd.csic.es
date: "2023-11-20"
output: html_document
format: 
   pdf:
      documentclass: article
      papersize: a4
      classoption: [11pt]
      fig-width: 8
      fig-height: 6
      geometry:
        - top=20mm
        - left=25mm
        - right=15mm
        - bottom=20mm
        - textwidth=130mm
code-fold: TRUE
bibliography: grateful-muxViz-refs.bib
editor_options: 
      chunk_output_type: console
---

```{r setup, echo=TRUE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(dplyr)
library(bipartite)
library(multinet)
library(muxViz)
library(emln)
library(infomapecology)
library(igraph)
library(MuMIn)
library(mgcv)
library(performance)
library(rsq)
library(lme4)
library(GGally)
library(grid)
library(gridExtra)
library(cowplot)
library(intergraph)
library(RColorBrewer)
library(viridis)
library(ggraph)
library(ggbipart)
library(ggcorrplot)
library(kableExtra)

# Setup paths to external fanmod and infomap executables.
pathFanmod <- here::here("./RCode/multiplex/src-exe/fanmod_macosx")
pathInfomap <- here::here("./RCode/multiplex/src-exe/infomap_macosx")

```

Here I analyze the data with `infomap`, basically, with some estimates obtained with
packages `elmn` and `muxViz`. Calculation of the multilayer metrics is done with package
`muxViz`.

First, interaction data are entered for the three interaction types as an edge list with
weights with all the interactions recorded.

## Data

Reading the original data adjacency matrices and summarizing species, interaction
frequencies, etc. to help assessing the large sparse matrices of te multilayer.

```{r input.prunus, echo=TRUE}
pm.disp<- read.table(here::here("data/raw/multiplex/pmah_disp.txt"), sep="\t",
                     dec=".", header= TRUE)
pm.poll<- read.table(here::here("data/raw/multiplex/pmah_poll.txt"), 
    na="NA", sep="\t", dec=".", header= TRUE)
pm.herb<- read.table(here::here("data/raw/multiplex/pmah_herb.txt"), 
     na="NA", sep="\t", dec=".", header= TRUE)
pm.attr<- read.table(here::here("data/raw/multiplex/pmah_attr.txt"), 
    na="NA", sep="\t", dec=".", header= TRUE)

# Interaction matrices extracted from the dataframes.
pm.herb.mat<- as.matrix(pm.herb[1:19,2:12], 
		ncol = n, dimnames = list(paste0("A", 1:12), paste0("P", 1:19)))
row.names(pm.herb.mat)<- pm.herb$X[1:19]

pm.poll.mat<- as.matrix(pm.poll[1:19,2:44], 
		dimnames = list(paste0("A", 1:44), paste0("P", 1:19)))
row.names(pm.poll.mat)<- pm.poll$X[1:19]

pm.disp.mat<- as.matrix(pm.disp[1:19,2:22], 
		dimnames = list(paste0("A", 1:22), paste0("P", 1:19)))
row.names(pm.disp.mat)<- pm.disp$X[1:19]

# Total number of distinct nodes (physical nodes). 
# Here the trees are counted just once.
dim(pm.herb.mat)[1]+dim(pm.herb.mat)[2]+dim(pm.poll.mat)[2]+dim(pm.disp.mat)[2]

# Total number of state nodes (trees). Here the trees are counted just once.
dim(pm.herb.mat)[1]

# Total number of nodes (physical and state). 
# Here the trees (state nodes) are counted three times, one state in each layer.
dim(pm.herb.mat)[1]+dim(pm.herb.mat)[2]+dim(pm.poll.mat)[1]+dim(pm.poll.mat)[2]+
    dim(pm.disp.mat)[1]+dim(pm.disp.mat)[2]

# Total number of interactions recorded
dim(pm.herb.mat); dim(pm.poll.mat); dim(pm.disp.mat)
sum(pm.herb.mat, pm.poll.mat, pm.disp.mat)

# Total number of distinct, pairwise interactions.
non_zero_count <- sum(pm.herb.mat != 0,   # Count non-zero elements. 
                                          # No. distinct interactions.
                      pm.poll.mat != 0, 
                      pm.disp.mat != 0) ; non_zero_count

```

Reading the multilayer network (dataframe) with columns indicating tree and animal species
(no,plant,animal,w,layer) and the following columns indicating the frequency of
interaction and the layer for each pairwise interaction.

Then I extract each interaction type and build layer-specific network graphs.

```{r data, echo=TRUE, fig.height=10, fig.width=14}
# Input all the interactions as a data.frame.
multilayer <- 
    read.csv(here::here("./data/raw/prunus_data/pmah_multilayer_data.csv"), 
             header = T)

# Edge list extended. For analysis in Infomap web app.
# Just open "./data/raw/prunus_data/pm_multilayer_net_explicit.csv" and
# copy/paste in web app.
# 

## Creating the layers by filtering the interactions mediated by each 
## type of resource.
#--------------------------------------------------------------------------
# Layer 1 - Herbivory interactions
ml1r <- multilayer %>% dplyr::filter(layer == "H") %>% 
	                  dplyr::select(plant, animal, w)
# List with plant and animal names
nodesH <- unique(c(as.character(unique(ml1r$plant)), 
                   as.character(unique(ml1r$animal))))

# igraph. Scaled weights.
scl.w <- ml1r$w*log(ml1r$w + 1) / max(ml1r$w + 1)

# Plotting the first layer in igraph
pru.herb.g <- graph_from_data_frame(ml1r, directed = FALSE,
									vertices = nodesH) %>%
                        set_vertex_attr(name = "types",
                        				value = names(V(.)) %in%
                        					    ml1r$plant)
E(pru.herb.g)$scl.w <- scl.w
V(pru.herb.g)$type <- bipartite_mapping(pru.herb.g)$type
V(pru.herb.g)$color <- ifelse(V(pru.herb.g)$type, "#4E98C9", "#E6C74C")
V(pru.herb.g)$shape <- ifelse(V(pru.herb.g)$type, "circle", "square")

is_weighted(pru.herb.g)

# Plot.
pm.herb.net<- bip_init_network(pm.herb.mat)
wt<- pm.herb.net %e% "weights"
wt<- wt*log(wt+1)/max(wt+1)
pm.herb.net %e% "weights"<- sqrt(wt)
col <- c(A="#4E98C9", P="#E6C74C")
pp1<- GGally::ggnet2(pm.herb.net, 
                     mode = "kamadakawai",
                     label=F, 
                     color = "mode", 
                     shape= "mode", 
                     palette = col, 
                     size = 8,
                     edge.color = "grey60", 
                     edge.size = "weights") +
       geom_label(aes(label = label), nudge_y = 0.045)
pp1

#--------------------------------------------------------------------------
# Layer 2 - Pollination interactions
ml2r <- multilayer %>% dplyr::filter(layer == "P") %>%
	                  dplyr::select(plant, animal, w)

nodesP <- unique(c(as.character(unique(ml2r$plant)), 
                   as.character(unique(ml2r$animal))))

# igraph. Scaled weights.
scl.w <- ml2r$w*log(ml2r$w + 1) / max(ml2r$w + 1)

# Plotting the first layer in igraph
pru.poll.g <- graph_from_data_frame(ml2r, directed = FALSE,
									vertices = nodesP) %>%
                        set_vertex_attr(name = "types",
                        				value = names(V(.)) %in%
                        					    ml2r$plant)
E(pru.poll.g)$scl.w <- scl.w
V(pru.poll.g)$type <- bipartite_mapping(pru.poll.g)$type
V(pru.poll.g)$color <- ifelse(V(pru.poll.g)$type, "lightblue", "yellow")
V(pru.poll.g)$shape <- ifelse(V(pru.poll.g)$type, "circle", "square")

is_weighted(pru.poll.g)

# Plot. NOT RUN
# igraph::plot.igraph(pru.poll.g,
#          layout=layout.fruchterman.reingold,
#          # layout= layout.kamada.kawai,
#          vertex.color= V(pru.poll.g)$color,
#          #vertex.color=c(rep("#FC9272", dim(mymat)[1]),
#          #               rep("#9ECAE1", dim(mymat)[2])),
#          vertex.size= 6,
#     	 vertex.label.dist= 1,
#          vertex.shape= V(pru.poll.g)$shape,
# 		 vertex.label.family= "sans",
#          edge.width= 7*scl.w)       # Adjust constant for
#                                     # better line widths
#                                     # edge.width=E(g)$weight/20)

# Plot.
pm.poll.net<- bip_init_network(pm.poll.mat)
wt<- pm.poll.net %e% "weights"
wt<- wt*log(wt + 1)/max(wt + 1)
pm.poll.net %e% "weights"<- sqrt(wt)
col <- c(A="#4E98C9", P="#E6C74C")
pp2<- GGally::ggnet2(pm.poll.net, 
                     mode = "kamadakawai",
                     label=F, 
                     color = "mode", 
                     shape= "mode", 
                     palette = col, 
                     size = 8,
                     edge.color = "grey60", 
                     edge.size = "weights") +
       geom_label(aes(label = label), nudge_y = 0.045)
pp2
   
#--------------------------------------------------------------------------
# Layer 3 - Seed dispersal interactions
ml3r <- multilayer |> dplyr::filter(layer == "SD") %>% 
    	              dplyr::select(plant, animal, w)

nodesSD <- unique(c(as.character(unique(ml3r$plant)), 
					as.character(unique(ml3r$animal))))

# igraph. Scaled weights.
scl.w <- ml3r$w*log(ml3r$w + 1) / max(ml3r$w + 1)

pru.disp.g <- graph_from_data_frame(ml3r, directed = FALSE,
									vertices = nodesSD) %>%
                        set_vertex_attr(name = "types",
                        				value = names(V(.)) %in%
                        					    ml3r$plant)
E(pru.disp.g)$scl.w <- scl.w
V(pru.disp.g)$type <- bipartite_mapping(pru.disp.g)$type
V(pru.disp.g)$color <- ifelse(V(pru.disp.g)$type, "lightblue", "salmon")
V(pru.disp.g)$shape <- ifelse(V(pru.disp.g)$type, "circle", "square")

is_weighted(pru.disp.g)

# # Plot. NOT RUN
# igraph::plot.igraph(pru.disp.g,
#          layout=layout.fruchterman.reingold,
#          # layout= layout.kamada.kawai,
#          vertex.color= V(pru.disp.g)$color,
#          #vertex.color=c(rep("#FC9272", dim(mymat)[1]),
#          #               rep("#9ECAE1", dim(mymat)[2])),
#          vertex.size= 6,
#     	 vertex.label.dist= 1,
#          vertex.shape= V(pru.disp.g)$shape,
# 		 vertex.label.family= "sans",
#          edge.width= 7*scl.w)       # Adjust constant for
#                                     # better line widths
#                                     # edge.width=E(g)$weight/20)
# Plot.
pm.disp.net<- bip_init_network(pm.disp.mat)
wt<- pm.disp.net %e% "weights"
wt<- wt*log(wt + 1)/max(wt + 1)
pm.disp.net %e% "weights"<- sqrt(wt)
col <- c(A="#4E98C9", P="#E6C74C")
pp3<- GGally::ggnet2(pm.disp.net, 
                     mode = "kamadakawai",
                     label=F, 
                     color = "mode", 
                     shape= "mode", 
                     palette = col, 
                     size = 8,
                     edge.color = "grey60", 
                     edge.size = "weights") +
       geom_label(aes(label = label), nudge_y = 0.04)
pp3

#---------------------------------------
# Plot in grid. 
# grid.arrange(pp1, pp2, pp3, nrow = 3)

```

## Multilayer network

Building the multilayer network object in `muxViz` from a series of edge lists for each
layer.

```{r multlyr, echo=TRUE, fig.height=10, fig.width=14}
# Generating the multilayer network joining all the layers.
# Naming layers.
Layer1Name <- "Herbivory"
Layer2Name <- "Pollination"
Layer3Name <- "Seed dispersal"

# Empty object for including the multilayer network.
net <- ml_empty()

# Add the layers in the empty object for generating multilayer network.
add_igraph_layer_ml(net, pru.herb.g, Layer1Name)
add_igraph_layer_ml(net, pru.poll.g, Layer2Name)
add_igraph_layer_ml(net, pru.disp.g, Layer3Name)

#--------------------------------------------------------------------------
### Preparing the data and files for using in muxViz package.
# Naming file to insert the network (data_config.txt), to indicate the 
# nodes as well the layers.
DataConfig  <- here::here("./RCode/multiplex/muxViz_infomap/input/data_config.txt")
NodesLayout <- here::here("./RCode/multiplex/muxViz_infomap/input/nodes_layout.txt")
LayerEdges1 <- here::here("./RCode/multiplex/muxViz_infomap/input/layer1.edges")
LayerEdges2 <- here::here("./RCode/multiplex/muxViz_infomap/input/layer2.edges")
LayerEdges3 <- here::here("./RCode/multiplex/muxViz_infomap/input/layer3.edges")

## Nodes layout.
# Creating the file with species name and ID. For this, we need to select 
# each species name once. We can organiza in alphabetical order using 
# the function "sort".
NodesMV <- as.data.frame(sort(unique(c(nodesH, nodesP, nodesSD))))

# Enumerating the nodes.
NodesMV <- cbind(1:nrow(NodesMV), NodesMV)

# Changing the column name (node ID and the species name).
colnames(NodesMV) <- c("nodeID", "nodeLabel")

# Saving the datframe.
write.table(NodesMV, NodesLayout, sep=" ", row.names=FALSE, quote=FALSE)

NodesMV.tib<- as_tibble(NodesMV)

#--------------------------------------------------------------------------
## Layer 1.
mll1 <- ml1r

# Including node label and species identity in layer 1
mll1[] <- lapply(mll1, function(z) {
  newval <- NodesMV$nodeID[match(z, NodesMV$nodeLabel)]
  ifelse(is.na(newval), z, newval)})

write.table(mll1, LayerEdges1, sep=" ", col.names = FALSE, 
            row.names=FALSE, quote=FALSE)

## Layer 2.
mll2 <- ml2r

mll2[] <- lapply(mll2, function(z) {
  newval <- NodesMV$nodeID[match(z, NodesMV$nodeLabel)]
  ifelse(is.na(newval), z, newval)})

write.table(mll2, LayerEdges2, sep=" ", col.names = FALSE, 
            row.names=FALSE, quote=FALSE)

## Layer 3.
mll3 <- ml3r

mll3[] <- lapply(mll3, function(z) {
  newval <- NodesMV$nodeID[match(z, NodesMV$nodeLabel)]
  ifelse(is.na(newval), z, newval)})

write.table(mll3, LayerEdges3, sep=" ", col.names = FALSE, 
            row.names=FALSE, quote=FALSE)

## Creating the data_config file.
LEdg1 <- paste(LayerEdges1, Layer1Name, NodesLayout, sep = ";")
LEdg2 <- paste(LayerEdges2, Layer2Name, NodesLayout, sep = ";")
LEdg3 <- paste(LayerEdges3, Layer3Name, NodesLayout, sep = ";")
LEdgAll <- c(LEdg1, LEdg2, LEdg3)

write.table(LEdgAll, DataConfig, sep="", col.names = FALSE, 
            row.names=FALSE, quote=FALSE)
#--------------------------------------------------------------------------
## Multilayer tensors

config.file <- here::here("./RCode/multiplex/muxViz_infomap/input/data_config.txt")

# config.file <- 
# "~/Documents/Working/MS_Multiplex_networks/data-raw/muxViz
# /pmah/pm_config.txt"
#
# This flag is important to understand if input networks are directed or not
isDirected <- F

# This flag is important to understand if input networks are weighted or not
isWeighted <- T

networkOfLayersType <- "ordinal"

# Indicating coupling strength in each layer (balanced strength for each layer)
LayerCouplingStrength <- 0.5

# Building a multilayer network in MuxViz package.
source(here::here("./RCode/functions/buildMultilayerNetworkFromMuxvizFiles_corrected.R"))
pm.mux <- buildMultilayerNetworkFromMuxvizFiles_corrected(
	                        config.file= config.file,
                            isDirected=isDirected,
                            isWeighted=isWeighted,
                            MultisliceType=networkOfLayersType,
                            LayerCouplingStrength=LayerCouplingStrength,
                            format="muxviz edge-colored",
                            verbose=T)
image(pm.mux$aggregateTensor, main = "dgCMatrix Heatmap", xlab = "Columns", ylab = "Rows")

# Build the multilayer adjacency tensor
M <- BuildSupraAdjacencyMatrixFromEdgeColoredMatrices(pm.mux$nodeTensor, pm.mux$layerTensor,
                                                      Layers= 3, Nodes= 94)
# lay <- layoutMultiplex(g.list, layout="fr", ggplot.format=F, box=T)

# Build the multilayer adjacency tensor
M <- BuildSupraAdjacencyMatrixFromEdgeColoredMatrices(pm.mux$nodeTensor,
                                                      pm.mux$layerTensor, Layers=3, Nodes= 94)
# Plot the supra-adjacency matrix
#image(M, main = "dgCMatrix Heatmap", xlab = "Columns", ylab = "Rows")
# Heatmap(M)

```

This is the multilayer adjacency tensor, showing interactions for N= 19 trees (rows 55 to
73) with herbivores, pollinators, and frugivores. These animal/fungi organisms are
arranged alphabetically as columns, according to the follwing list.

```{r adj.tensor_list, echo=TRUE}
# TODO: Arrange this tibble as trees, herb, poll, disp.
NodesMV.tib

```

# Multilayer layout

Input the multilayer data and layout. Analysis and evaluation with the multilayer network.

```{r multlyr_layout, echo=TRUE, fig.height= 10, fig.width= 14}
#--------------------------------------------------------------------------
## Multilayer metrics
# Build supraadjacency matrix.
pm.mEdges <- 
    read.csv(here::here("./data/raw/multiplex/pm_supraadj.edges"),
             header = TRUE, sep=",", dec=".")
#Change the column name - id to c1
pm.mEdges<- pm.mEdges %>% 
   rename("node_from" = "node.from")   %>%
   rename("layer_from" = "layer.from") %>%
   rename("node_to" = "node.to") %>%
   rename("layer_to" = "layer.to") 

pm.mEdges.tib<- as_tibble(pm.mEdges)
pm.mEdges.tib<- pm.mEdges.tib %>% relocate(node_from, .after = layer_from)
pm.mEdges.tib<- pm.mEdges.tib %>% relocate(node_to, .after = layer_to)

pm.supramux<- BuildSupraAdjacencyMatrixFromExtendedEdgelist(
  pm.mEdges,
  3,
  94,
  isDirected= FALSE
)

pm.nodes.tns<- SupraAdjacencyToNodesTensor(pm.supramux, Layers=3, Nodes=94)

# Scaled weights.
    mlr<- as.data.frame(rbind(ml1r, ml2r, ml3r))
    scl.w <- ml1r$w*log(mlr$w + 1) / max(mlr$w + 1)

pm.supraadj.g<- GetAggregateNetworkFromSupraAdjacencyMatrix(pm.supramux, 3, 94)
bipartite_mapping(pm.supraadj.g)
E(pm.supraadj.g)$scl.w <- scl.w
V(pm.supraadj.g)$type <- bipartite_mapping(pm.supraadj.g)$type
V(pm.supraadj.g)$color <- ifelse(V(pm.supraadj.g)$type, "lightblue", "salmon")
V(pm.supraadj.g)$shape <- ifelse(V(pm.supraadj.g)$type, "circle", "square")
V(pm.supraadj.g)$layer <- c(rep("tree",19), 
								rep("H",11),
								rep("P",43),
								rep("SD",21))
V(pm.supraadj.g)$ly.color <-  c(rep("yellow",19), 
								rep("lightblue",11),
								rep("orange",43),
								rep("salmon",21))

# Plot the sparse matrix.
image(pm.supramux, main = "dgCMatrix Heatmap", xlab = "Columns", ylab = "Rows")

#--------------------------------------------------------------------------

```

Here we see the three layers of interactions as rectangles in the symmetric supra-matrix.
Each adjacency matrix canbe seen in the upper-diagonal matrix as rectangles with trees as
rows and animal/fungi organisms as columns (e.g., trees as rows 1-19, 95-113, and
190-208). The diagonal lines to the sides represent the interlayer links.

# Compute some multilayer statistics

```{r centrality_measures}
# PageRank centrality
pr <- GetMultiPageRankCentrality(pm.supramux, Layers= 3, Nodes= 94)

# Eigenvector centrality
egvC<- GetMultiEigenvectorCentrality(pm.supramux, Layers= 3, Nodes= 94)

# Multidegree
multidegree<- GetMultiDegree(pm.supramux, Layers= 3, Nodes= 94, isDirected=F)

# Multistrength
multistrength<- GetMultiInStrength(pm.supramux, Layers= 3, Nodes= 94, isDirected = F)

# List of three igraph objects for the thre mnanolayers.
g.list<- SupraAdjacencyToNetworkList(pm.supramux, Layers=3, Nodes=94)

# Saving multilayer muxViz statistics.
node<- NodesMV.tib$nodeLabel
muxViz_stats <- as.data.frame(cbind(node, pr, egvC, multistrength, multidegree))
colnames(muxViz_stats)<-c("node","pagerankcentrality",
                          "eigenvectorcentrality","multistrength",
                          "multidegree") 

# Output to table.
write.table(muxViz_stats,
            here::here("./RCode/multiplex/muxViz_infomap/out/muxViz_stats.txt"), 
            sep=",", col.names = TRUE, row.names=TRUE, quote=FALSE)


# muxViz_stats %>% kableExtra::kable(digits = 4) %>%
#kableExtra::kable_styling(font_size = 10, latex_options = "scale_down")

# Pearson and Spearman correlation coefficients among layers.
pm.assort.tnsr<- GetInterAssortativityTensor(
  pm.supramux,
  Layers= 3,
  Nodes= 94,
  isDirected= F,
  Type="TT"
)               ; pm.assort.tnsr

# Similarity matrix among layers.
pm.sim.mat<- GetSPSimilarityMatrix(pm.supramux, Layers=3, Nodes= 94)
pm.sim.mat


```

## Multilayer metrics

# Metrics with muxViz

I'm using here the shell version of Infomap. It is run in the terminal with output files
directed to directory `./out`.

```{r infomap-shell, echo=TRUE, fig.width=14,fig.height=9}
# RUN THIS COMMAND IN TERMINAL:
system("ls -l")
system("./Infomap ./out/multimap_prunus_infomap.edges ./out/ --clu --seed 12345 --num-trials 50 -v --multilayer-relax-rate 0.45, multilayerJSRelaxRate= NA, --two-level outputPrefix= multimap_prunus")

```

### Draft for metrics storage

Here I pool the combined multilayer stats for different species and the trees in order to
obtain estiamtes of strength and centrality for each taxa within the multilayer structure.

```{r metrics_storage, echo=TRUE}
# Creating files to store metrics
# We will evaluate metrics from different perspectives (multilayer, aggregate and
#  single-layer).

# Multilayer perspective

res <- data.frame()

res[["degree"]] <- data.frame()
res[["strength"]] <- data.frame()
res[["pagerank"]] <- data.frame()
res[["eigcentr"]] <- data.frame()
# res[["avglobclust"]] <- data.frame()
res[["conncomp"]] <- data.frame()

# Obtaining multilayer metrics
multi.deg <- GetMultiDegree(pm.supramux, Layers= 3, 
                            Nodes= 94, 
                            isDirected = F)
multi.str<- GetMultiStrength(pm.supramux, Layers= 3, 
                             Nodes= 94, 
							 isDirected= F)
# multi.in.deg<- GetMultiInDegree(pm.supramux, Layers= 3, 
#								Nodes= 94, isDirected = F)
# multi.in.str<- GetMultiInStrength(pm.supramux, Layers= 3, Nodes= 94, 
#							  isDirected= F)
multi.PR.cent <- GetMultiPageRankCentrality(pm.supramux, Layers= 3, 
                                           Nodes= 94)
multi.egv.cent<- GetMultiEigenvectorCentrality(pm.supramux, 
                                               Layers= 3, Nodes= 94)
# multi.Kcore.cent<- GetMultiKCoreCentrality(pm.supramux, Layers= 3, 
#                                           Nodes= 94)
# avg.glob.clust<- GetAverageGlobalClustering(pm.supramux, Layers= 3, 
#                                            Nodes= 94)
# conn.comp<- GetConnectedComponents(pm.supramux, Layers= 3,
#                                   Nodes= 94)

res <- data.frame(node= NodesMV$nodeLabel, 
				  multidegree= multi.deg,
				  multistrength= multi.str,
#				  multiindeg= multi.in.deg,
#				  multiinstr= multi.in.str,
				  multiPRcent= multi.PR.cent,
				  multiegvcent= multi.egv.cent)
# 				  multiKcorecent= multi.Kcore.cent)
#				  avglobclust= avg.glob.clust,
#				  conncomp= conn.comp)
# res

res %>% kableExtra::kable(digits = 4) %>%
            kableExtra::kable_styling(font_size = 11, latex_options = "scale_down")

# Output to table.
write.table(res, here::here("./RCode/multiplex/muxViz_infomap/out/muxViz_multistats.txt"), 
            sep=",", col.names = TRUE, row.names=TRUE, quote=FALSE)

```

------------------------------------------------------------------------------------------

# `R` packages used

```{r grateful, echo: F, message: F, class.message: F, class.warning: F, warning: F}
pkgs <- grateful::cite_packages(output = "table", pkgs = "Session", out.dir = ".")
knitr::kable(pkgs)

```

{{< pagebreak >}}

Session info

```{r session, warning=FALSE, error=FALSE}
sessionInfo()

```

{{< pagebreak >}}

# References
